Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
edit

\cite{Bailin05} used seven hydrodinamical simulations studied the disc
halo alignmnent as a function of radius.
For radii smaller than $0.1R_{200}$ they find a strong alignment
between the two minor axis of the halo and the disc. 
For larger radii the angle between the components changes showing a
weak correlation between the two components. 
\cite{Debattista13} performed a study on the disc-halo aligment
performing controled experiments on three different halos to study
changes the evolutionary change that drive the minor axis in the disc
and the halo to be aligned, their study by construction focuses only
on radii around $0.1R_{200}$.
Nevertheless, similarly to \cite{Bailin05}, they also report a strong
alignment in the region where the disc dominated.

\cite{Gomez17} studied this in Auriga.

>>>>

\cite{Bailin05} used seven hydrodinamical simulations studied the disc
halo alignmnent as a function of radius.
For radii smaller than $0.1R_{200}$ they find a strong alignment
between the two minor axis of the halo and the disc. 
For larger radii the angle between the components changes showing a
weak correlation between the two components. 
\cite{Debattista13} performed a study on the disc-halo aligment
performing controled experiments on three different halos to study
changes the evolutionary change that drive the minor axis in the disc
and the halo to be aligned, their study by construction focuses only
on radii around $0.1R_{200}$.
Nevertheless, similarly to \cite{Bailin05}, they also report a strong
alignment in the region where the disc dominated. 
In conclusion, the twisting in the dark matter halo shapes seems to be
a feature already reported in the literature with smaller samples than
the one we use here. 
The strongest point of depart is that in our case the alignments do
not grow stronger as one approached the disc.
It is very likely that the detailed radial dependence of the twisting
depends on the hydrodynamics and feedback implementations.
